---
title: "JSC370 Homework5 temp"
author: "Naihe Xiao"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

<br>

This is my JSC370 homework5 website. I will showcase the 3 interactive visuals I created.

<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(plotly)
library(knitr)
library(widgetframe)
library(dplyr)
library(tidyr)
library(ggplot2)

# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

<br>
## First plot
```{r plot1, class.source="code-r-small"}
data <- read.csv("https://raw.githubusercontent.com/dabandaidai/JSC370-project/main/acs2017_census_tract_data.csv")
sort_by_pop <- data %>% 
  arrange(desc(TotalPop))
sort_by_pop <- head(sort_by_pop, 100)
plt1 <- plot_ly(
  sort_by_pop,
  x = ~ Income,
  y = ~ log(Unemployment),
  color = ~ State,
  size = ~ TotalPop,
  mode = 'markers',
  type = "scatter",
  sizes = c(10, 50),
  marker = list(sizemode = "area", 
                opacity = .8),
  hoverinfo = "text", 
  text = ~ paste0(
                  State, "\n",
                  "   County: ", County, "\n",
                  "   Poverty: ", Poverty, "\n",
                  "   Men: ", Men, "\n",
                  "   Women: ", Women, "\n",
                  "   MeanCommute: ", MeanCommute
                )
)
```

The plot shows the relationship between the income and the log unemployment rate(since the histogram of unemployment shows heavy skewness) for the top 100 most populated states in the data frame, where each point contains information about the state, mean commute time, poverty rate, number of men and number of women in the tract. The size of each point is determined by the total population of the state, and the color of the point represents the state. This plot illustrate some interesting features:
* There are two tracts with particularly low unemployment rate: one in salt lake county in Utah and one in ada county in Idaho. Reasonably, these two tracts all have relatively low poverty rate and shorter mean commute time(in minutes). 
* As the income increases, the unemployment rate seems to be a slight tendency of decreasing, especially when income is in the range from 40k to 100k.
* There does not seem to be a relationship between the population of the tract and the unemployment rate according to the size of the balls. 
* It seems like Texas and Florida contains the highest number of the most populated tracts.

## Second plot

Note: You need to name each code chunk, like this one: `plot1`

```{r plot2, class.source="code-r-small"}
plt_smooth <- ggplot(
  sort_by_pop,
  aes(x = MeanCommute, y = log(Unemployment))
) +
  geom_point(aes(colour = State, size = TotalPop)) + 
  geom_smooth() +
  theme_minimal() +
  scale_x_continuous(trans = "log")
plt2 <- ggplotly(plt_smooth)
```
The plot shows the relationship between the mean commute time (in minutes) and the log unemployment rate(again, due to skewness) for the top 100 most populated states in the data frame. The size of each point is determined by the total population of the state, and the color of the point represents the state.

According to the fitted smoothed line, there are no monotone relationship between the mean commute time and unemployment rate: in fact as the mean commute time decreases from 14.7 minutes to 30 minutes, the unemployments decreases; however, as the mean commute time increases from 30 minutes to 50 minutes the unemployment rises again.

<br>

## Third plot
```{r plot3, class.source="code-r-small"}
data$abb <- state.abb[match(data$State,state.name)]
data$Unemployment2 <- data$Unemployment * 2
map <- plot_geo(
  data,
  locationmode = "USA-states"
) %>% 
  add_trace(
    z = ~ Unemployment,
    locations = ~ abb
  ) %>% 
  layout(
    geo = list(
      scope = "usa",
      showlakes = TRUE,
      lakecolor = toRGB("darkgrey")
    )
  )
```

From the map I observe that the unemployment rate in each state is approximately even, ranging from 0 to 20 percent. In general, the states in the middle area have lower unemployment rate than the states in the south and south east, and South Dakota seems to standout by having an unemployment rate that is obviously higher than any other states.


## Illustration {.tabset}

Create tabs to display each figure

### First Scatterplot

```{r p1}
plt1
```

### Second Scatterplot

```{r p2}
plt2 
```

### Map

```{r}
map
```

## {-}

<br>

Done with my homework 5.

<br>
<br>
